Dataset Summary

### 2019-08-01 scripts/old scripts/2018.07.01-Overview.Rmd
Rename scripts/2018.07.01-Overview.Rmd to scripts/old scripts/2018.07.01-Overview.Rmd

```{r setup, include=FALSE, echo=TRUE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
library(readr)
library(dplyr)
library(skimr)
library(ggplot2)
library(scales)
library(viridis)
library(knitr)
library(kableExtra)
```

@@

>>>>

```{r setup, include=FALSE, echo=TRUE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE, cache=FALSE)
root.dir = rprojroot::find_root("README.md")
knitr::opts_knit$set(root.dir = root.dir)

library(readr)
library(dplyr)
library(skimr)
library(ggplot2)
library(scales)
library(viridis)
library(knitr)
library(kableExtra)
```

@@

# Datasource

more recently, Jeremy states: "I provided you too much data (!) which should not be included.  A quarter to a third of the data is from legacy projects and should be excluded.  As I mentioned, exclude anything without datasource_name = `IMPC`"

By source: 
```
data_raw$datasource_name %>% table()
```

So reducing to IMPC reduces the data by one third.

It also greatly reduces the number of parameters:
```{r}
filter(data_raw, datasource_name == 'IMPC') %>% pull(parameter_name) %>% unique() %>% length()
```

```
data_raw %>% pull(parameter_name) %>% unique() %>% length()
```
